---
title: My First Markdown Document
author: The Medium R Crew
date: The Best Day Ever
output: html_document
---

# First Section

We just created our first section in this document. Spacing is very important in markdown, so we left a blank line after the hash tag.

We create a new paragraph by leaving a blank line. See how important spaces are in markdown?

# Second Section

To create a new section, simply start a new section. No need to clost the previous section. Again, leave spaces.

# Let's Talk About Subsections

To create a subection, use two hashtags.

## First Subsection

We now have a subsection in the enclosing section.

## Second Section

To start a new subsection, simply start a new one, no closing the old one, just like wtih sections.

# Back to Sections

Return to sections just by starting a new section. Very simple.

# Lists

## Unordered Lists

- Apples
- Bananas
- Oranges
- Kiwis

## Ordered Lists

1. New York
1. New Jersey
1. Naples
1. Detroit
1. Rome

And now we show a sublist example

1. New York
    1. Coal
    1. Wood
    1. Gas
1. New Jersey
    1. Gas
    1. Wood
1. Detroit
    1. Gas
    1. Electric
1. Naples
    1. Wood
1. Philadelphia
1. Rome

a. Coal
a. Wood
a. Gas

# Formatting

_Text in here is emphasized_

__This will be strong text__

___This will be both emphasized and strong___

`This is code text`

# Links

[Link to my website](http://www.jaredlander.com)

# R Time!!!!!!

```{r addition}
1 + 1
```

```{r variables}
x <- 3
x
```

Let's see if that variable `x` is available in other junks.

```{r multiplication}
x*2
```

# Plots

```{r histogram,echo=FALSE}
library(ggplot2)

ggplot(diamonds, aes(x=price)) + geom_histogram()
```

